# Distribution Plot: Histogram & Density Plot

## Simple Histogram
 - `binwidth`refers the width of the interval.  
 - If `binwidth = 2`, and your data ranges from 0 to 10, the bins would be: 0–2, 2–4, 4–6, 6–8, 8–10.
```{r}
data |> 
  ggplot(aes(x = BMI)) + 
  geom_histogram(color = "black", binwidth = 2)
```

## Grouped Histogram
- In `position` it can be `identity`, `stack`, `dodge`, `fill`
```{r}
data |> 
  ggplot(aes(x = BMI, fill = Gender)) + 
  geom_histogram(color = "black", binwidth = 2, position = "stack")
```

## Grouped in multiple plot
- `facet_wrap` is a function that can divide two groups.
- In this function default wrapping variable must be included.
```{r}
data |> 
  ggplot(aes(x = BMI, fill = Gender)) + 
  geom_histogram(color = "black", bins = 10, binwidth = 2)+
  facet_wrap(~Gender)
```



## Simple Density Plot
```{r}
data |> 
  ggplot(aes(x = BMI)) + 
  geom_density()
```
## Grouped Density plot
```{r}
data |> 
  ggplot(aes(x = BMI, fill = Gender)) + 
  geom_density()
```




## Grouped in multiple plot
```{r}
data |> 
  ggplot(aes(x = BMI, fill = Gender)) + 
  geom_density()+
  facet_wrap(~Gender)
```


## Histgram with Density Curve
```{r}
data |> 
  ggplot(aes(x = BMI, fill = Gender, color = Gender))+
  geom_histogram(aes(y = ..density..), alpha = 0.5, binwidth = 2, bins = 10, position = "identity")+
  geom_density(alpha = .5)+
  facet_wrap(~Gender)
```

