# Customization
- Customization is more or less same in all plot conducted through ggplot2 package.

## Simple Customization
```{r}
data |> 
  ggplot(aes(x = BMICat, fill = Gender))+
  geom_bar()+
  labs( x = "BMI Category",
        y = "Frequency",
        title = "Distribution of BMI category across Gender",
        subtitle = "This figure shows the BMI category based on gender",
        caption = "Data Source: CHIRAL")
```
## Themes (Step: 1)
 - First we need load some packages
```{r}
# Load necessary packages
library(ggthemes)
library(hrbrthemes)
library(ggsci)
```

## Themes (Step: 2)
 - Then we need to store the visualization file in a variable
```{r}
# store  in a variable
Visual <- data |> 
  ggplot(aes(x = BMICat, fill = Gender))+
  geom_bar()+
  labs( x = "BMI Category",
        y = "Frequency",
        title = "Distribution of BMI category across Gender",
        subtitle = "This figure shows the BMI category based on gender",
        caption = "Data Source: CHIRAL")
```

## Themes (Step: 3)
 - Now we can simply perform theme
```{r}
# Now we can just add themes with the variable
 Visual + theme_economist()
```

## Available Color Fill
```{r}
Visual + scale_fill_colorblind()
```

## Manual Color Fill
```{r}
Visual + scale_fill_manual(values = c("#0868ac", "#006d2c"))
```

## Set font size & family
```{r}
Visual + theme_base(base_size = 11, base_family = "Algerian")
```

## Font size for labels, tick labels, and legend separately
- Both
```{r}
Visual + theme(axis.title = element_text(size = 40))

```

## Font size for labels, tick labels, and legend separately
- only x-axis
```{r}
Visual + theme(axis.title.x = element_text(size = 40))
# For y-axis
# basic + theme(axis.title.y = element_text(size = 40))

```
## Font size for title and subtitle
```{r}
Visual + theme(plot.title = element_text(size = 40))

# basic + theme(plot.title = element_text(size = 40))
# basic + theme(plot.title = element_text(size = 40),  plot.subtitle = element_text(size = 40)

```


## Customize legend
```{r}
Visual + theme(legend.position = "top")
```



