# Bar Chrat
## Simple Bar Charts 
 - A barplot shows the relationship between a numeric and a categorical variable.
 - Each entity of the categoric variable is represented as a bar. 
 - The size of the bar represents its numeric value.

## Purpose Simple Bar Charts
 - To describe the number of observations in each category of the discrete variable.
 - To visualize estimated error for discrete variables.

## Simple Bar Chart (Vertical Orientation)
```{r}
# For a Single Categorical Variable
library(ggplot2)
data |> 
  ggplot(aes(x = BMICat))+
  geom_bar()

```
## Simple Bar Charts (Horizontal)
```{r}
data |> 
  ggplot(aes(x = BMICat))+
  geom_bar()+
  coord_flip()
```


## Sorting Bar Chart
- For sort down ascending order we can just use `fct_reorder()` from `forcats` package. 
- .fun = length counts the number of occurrences for each level in BMICat.
```{r}
data |> 
  ggplot(aes(x = forcats::fct_reorder(BMICat, BMICat, .fun = length)))+
  geom_bar()
  
```


## Grouped Bar Chart
 - Grouped bar charts are used to compare multiple categories across multiple groups
```{r}
data |> 
  ggplot(aes(x = BMICat, fill = Gender))+
  geom_bar()
```









